Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-07-11 abstract.tex
fix some problem.

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining  the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$ and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered as an alternative method for analyzing earthquake sequences. 
\end{abstract}

>>>>

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method. For purposes of this study, northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh. Using the declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e.  $< T_c >$, $k-M$ slope) of the network and dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope. The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences. 
\end{abstract}

%% Original text

%\begin{abstract}
%The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining  the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$ and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered as an alternative method for analyzing earthquake sequences. 
%\end{abstract}

### 2016-07-11 conclusion.tex
fix some problem.

\section{Conclusion}
\noindent
We studied the earthquake sequence of three tectonic seismic regions of north Iran. Results manifest the strong relationship between $k-M$ slope and Gutenberg-Richter parameters. The variation of $k-M$ slope and $b-value$ with time in sliding windows have similar behavior and drops down before big earthquakes. Significant reduction of $<T_C>$ value before big earthquake is observed. Higher coefficient of variation of $k-M$ slope in comparison with $b-value$, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$. In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.

>>>>

\section{Conclusion}
\noindent
We studied the earthquake sequence of three tectonic seismic regions of northern Iran. Results manifest the strong relationship between  $k-M$  slope and Gutenberg-Richter parameters. The variations of  $k-M$  slope and  b-value  with time in sliding windows have similar behavior and decline before large earthquakes. A significant reduction of  $<T_C>$  value before large earthquakes was observed. The higher coefficient of variation of  $k-M$  slope in comparison with  b-value  suggests that the  $k-M$  slope is a better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than  is found in the $b-value$. In general,  the $k-M$  and  $b-value$  relationship preserves the behavior with the variation in the window size and threshold magnitude, and could be an alternative approach for clustering earthquake sequences based on different tectonic seismic zones.

### 2016-07-11 introduction.tex
fix some problem.

\section{Introduction}
\noindent
\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs. Basically the visibility graph presents the connection between nodes in the network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other, if no other event interrupts their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
\end{equation}

\noindent
where, $y$ is the value and $t$ is the time of the event. $k$ is the index of any event occurring between event $i$ and event $j$. The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  and 3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}. This concept has applications ranging in various fields including geophysical studies.

\noindent
The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method. Applying different threshold magnitudes and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and to be independent of the threshold magnitude. In another research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through visibility graph approach. They extracted characteristics of the visibility graph for five different tectonic seismic regions.  According to their study, visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line fitting the Magnitude  of each event $(M)$ and its connectivity degree $(k)$) was investigated in their study. In a similar article, \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extracted the visibility graph characteristics for each class. According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient value (close to 1) of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , defined the $ <T_C>$, as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequence in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\

\noindent
In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region \citep{Nemati2015} . \\

\noindent
Northern Iran has an elaborate seismic history.  Having considerable number of earthquakes and also being in different tectonic seismic region, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions. We also investigate the variation of $<T_C>$ value through time.

>>>>

\section{Introduction}
\noindent
\citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs. Basically, the visibility graph presents the connection between nodes in a network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other if no other event interrupts their linear connection. In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
\end{equation}
\noindent
where $y$ is the value and $t$ is the time of the event, and $k$ is the index of any event occurring between events  $i$  and  $j$. The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}. This concept has applications in fields including geophysical studies. \\
\noindent
The analysis of seismic sequence through visibility graph for various tectonic seismic regions revealed an alternative approach to studying the magnitude time series.  \citet{Telesca2012} studied the seismic sequence of Italy between the years 2005 and 2010 using the visibility graph method. Applying different threshold magnitudes and observing the collapsing effect of all distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend on only the values of the magnitude and being independent of the threshold magnitude. 
\noindent
In other research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach. They extracted characteristics of the visibility graph for five different tectonic seismic regions.  According to their study, a visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes governing the area. Their study investigated the relationship between the Gutenberg-Richter parameters and the $k-M$ slope, which is the slope of the regression line fitting the magnitude of each event  ($M$) and its connectivity degree  ($k$). 
\noindent
In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph. They classified the seismic catalog into shallow and deep earthquakes, and extracted the visibility graph characteristics for each class. According to their study, a close relationship exists between the Gutenberg-Richter $b-value$ and the $k-M$ slope of the visibility graph. The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014} .   
\noindent
\citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India. They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary. In addition,  $<T_C>$  significantly decrees before the largest shock of the catalog. Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks. 
\noindent
In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions, namely Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view.  \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}. Northern Iran has an extensive seismic history.  Having a considerable number of earthquakes and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study, we present the relationship between  $k-M$  slope and $b-value$  in these three different tectonic seismic regions. We also investigate the variation of  $<T_C>$  value through time.

% Original text
%\section{Introduction}
%\noindent
%\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs. Basically the visibility graph presents the connection between nodes in the network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other, if no other event interrupts their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:
%
%\begin{equation}
%\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
%\end{equation}
%
%\noindent
%where, $y$ is the value and $t$ is the time of the event. $k$ is the index of any event occurring between event $i$ and event $j$. The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  and 3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}. This concept has applications ranging in various fields including geophysical studies.
%
%\noindent
%The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method. Applying different threshold magnitudes and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and to be independent of the threshold magnitude. In another research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through visibility graph approach. They extracted characteristics of the visibility graph for five different tectonic seismic regions.  According to their study, visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line fitting the Magnitude  of each event $(M)$ and its connectivity degree $(k)$) was investigated in their study. In a similar article, \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extracted the visibility graph characteristics for each class. According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient value (close to 1) of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , defined the $ <T_C>$, as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequence in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\
%
%\noindent
%In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region \citep{Nemati2015} . \\
%
%\noindent
%Northern Iran has an elaborate seismic history.  Having considerable number of earthquakes and also being in different tectonic seismic region, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions. We also investigate the variation of $<T_C>$ value through time.
%

### 2016-07-11 results.tex
fix some problem.

\section{Results}
\noindent
We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015. Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.

@@

\noindent
Fig.~\ref{fig:k_m_plot_m} shows the $k-M$ relationship for the study regions.  In general with increasing magnitude the connectivity degree increases which results in increasing the slope of the $k-M$ relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
\label{fig:k_m_plot_m}
\end{figure}

\noindent
We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time. The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.

@@

 \noindent
The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}. The $k-M$ slope shows higher coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.

 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.

@@

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

\noindent
\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.

@@

>>>>

\section{Results}
\noindent
We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period 2005-15. The number of earthquakes in each catalog after declustering and their seismicity parameters is presented in Table.~\ref{tab:b_k_m_param}.

@@

\noindent
Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.  In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
\label{fig:k_m_plot_m}
\end{figure}
 \noindent
We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time. The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}
 \noindent
where $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region. The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.  \citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope. Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.  According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes. The minimum size of random windows is 150 events. (Note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively.). The maximum size is the size of the entire catalog. For each randomly picked magnitude time series,  we estimated $Mc$,  and the  $k-M$  and $b-value$ were calculated. Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables. Although changing the number of events and the threshold magnitude is a slight change, the results are fairly well clustered for each tectonic seismic region.

@@

\noindent
The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}. The  $k-M$  slope shows the higher coefficient of variation. The  $k-M$  slope is more dependent on the window size and threshold magnitude than  on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series. 
 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and two other studies of Mexican zones  \citep{Telesca2013}  and Pannonia zones  \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.955), and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.

@@

\noindent
Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time. Having a lower number of events, we chose 20 events as the window length with a shift of one event between two successive windows. The calculated parameters of each window were associated with the time of occurrence of the last event in the sliding window. The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar. In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes. The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
\noindent
\citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence. Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area, and the decrease in  $<T_C>$   before a large earthquake is clearly visible.  \citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude. Fig.\ref{fig:tc}  shows the decrement in the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes.

@@

 % Original text
%\section{Results}
%\noindent
%We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015. Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}. 
%
%
%\begin{table}[h]
%\centering
%\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
%\begin{tabular}{ccccc}
%Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
%Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
%Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
%Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
%\end{tabular}
%\label{tab:b_k_m_param}
%\end{table}
%
%\noindent
%Fig.~\ref{fig:k_m_plot_m} shows the $k-M$ relationship for the study regions.  In general with increasing magnitude the connectivity degree increases which results in increasing the slope of the $k-M$ relationship. 
%
%\begin{figure} [ht]
%\centering
%\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
%\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
%\label{fig:k_m_plot_m}
%\end{figure}
%
%\noindent
%We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time. The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.
%
%\begin{equation}
%b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
%\end{equation}
% 
% \noindent
% where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region. 
% 
% \begin{figure} [ht]
%\centering
%\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
%\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
%\label{fig:random}
%\end{figure}
% 
% \noindent
%The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}. The $k-M$ slope shows higher coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series. 
% 
% 
%
% 
% \noindent
% Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded. 
%
%\begin{figure} [ht]
%\centering
%\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
%\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
%\label{fig:regression}
%\end{figure}
%
%
%\noindent 
%Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
%
%\noindent
%\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.
% 
% \begin{figure} [ht]
%\centering
%\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
%\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake.}
%\label{fig:tc}
%\end{figure}
